ExEl: Building an Elaborator Using Extensible Constraints

### 2024-03-22 paper/main.tex
add acm-provided info
sync paper with camera-ready

@@

\begin{acks}
  Jesper Cockx holds an \grantsponsor{nwoviveni202216}{NWO Veni}{https://www.nwo.nl/en/projects/viveni202216} grant on `A trustworthy and extensible core language for Agda' \grantnum[https://www.nwo.nl/en/projects/viveni202216]{nwoviveni202216}{(VI.Veni.202.216)}.
\end{acks}

>>>>

\copyrightyear{2023}
\acmYear{2023}
\setcopyright{rightsretained}
\acmConference[IFL 2023]{The 35th Symposium on Implementation and Application of Functional Languages}{August 29--31, 2023}{Braga, Portugal}
\acmBooktitle{The 35th Symposium on Implementation and Application of Functional Languages (IFL 2023), August 29--31, 2023, Braga, Portugal}
\acmDOI{10.1145/3652561.3652565}
\acmISBN{979-8-4007-1631-7/23/08}

@@

\begin{acks}
  Jesper Cockx holds an \grantsponsor{nwoviveni202216}{NWO Veni}{https://www.nwo.nl/en/projects/viveni202216} grant on `A trustworthy and extensible core language for Agda' (\href{https://www.nwo.nl/en/projects/viveni202216}{VI.Veni.202.216}).
\end{acks}
